Supplemental Materials for the paper: \\ Pesticide exposure in small streams in Germany

### 2016-10-20 cover_letter/cover.tex
revised supplement + cover

We compiled and homogenized monitoring data from all German Federal States with a focus on small streams. 
Our results show that:
\begin{enumerate} 
\item there is currently a lack of knowledge for small streams
\item the influence of agricultural land use is non-linear with a threshold at 25\%
\item measured pesticide concentrations increase by precipitation before sampling and therefore current monitoring underestimates risks
\item show compound specific yearly dynamics that corresponds to applications
\item especially, neonicotinoids pose a risk to small agricultural freshwaters.
\end{enumerate}

>>>>

We compiled and homogenized monitoring data from all German Federal States with a focus on small streams. 
Our results show that:
\begin{enumerate} 
\item regulatory threshold exceedances depend non-linearly on agricultural land use within the catchment
\item measured pesticide concentrations depend on precipitation events before sampling and therefore current monitoring underestimates risks
\item the annual dynamic of concentrations is compound-specific and corresponds to applications
\item especially, neonicotinoids pose a risk to small agricultural freshwaters.
\end{enumerate}

### 2016-10-20 supplement/Supplemental_Materials.tex
fix supplement and refs to supplement
revised supplement + cover

%% -------------------------------------------------------------------------
\title{Supplemental Materials for the paper: \\ Pesticide exposure in small streams in Germany}
\author{Eduard Szöcs, Marvin Brinke, Bilgin Karaoglan, Ralf B. Schäfer}

@@

\begin{enumerate}
	\item Structure: Structure has been adjusted to the database structure.
	\item Coordinates: Coordinates have been transformed to a common Coordinate Reference System (DHDN / 3-Grad Gauss-Krüger Zone 3 (EPSG:31467)) and duplicates merged.
	\item Chemicals: Chemical names and identifiers have been unified using the webchem package (\url{https://github.com/ropensci/webchem}).
	\item  Identifiers: Unique identifiers have been assigned.
	\item Units: All concentrations have been converted to $\mu g/L$. Values below limit of quantification have be set to zero.
	\item Other meta-data: meta-data has been standardised.
	\item Temporal resolution: The temporal resolution of the database is 1 day. Date below this resolution has been aggregated by maximum.
	\item Validity Checks: Simple rules for validity checks have been implemented (e.g. no negative concentrations).
\end{enumerate}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width = 0.8\textwidth]{pmix}
	\caption{Distribution the number of quantified compounds in the samples from small streams.}
	\label{fig:pmix}
\end{figure}

@@

>>>>

%% -------------------------------------------------------------------------
\title{Supplemental Materials for the paper: \\ Pesticide exposure in small streams in Germany}
\author{Eduard Szöcs, Marvin Brinke, Bilgin Karaoglan, Ralf B. Schäfer}
\date{}

@@

\begin{enumerate}
	\item Structure: Structure has been adjusted to the database structure.
	\item Coordinates: Coordinates have been transformed to a common Coordinate Reference System (DHDN / 3-Grad Gauss-Krüger Zone 3 (EPSG:31467)) and duplicates merged.
	\item Chemicals: Chemical names and identifiers have been unified using the webchem package (https://github.com/ropensci/webchem).
	\item  Identifiers: Unique identifiers have been assigned.
	\item Units: All concentrations have been converted to $\mu g/L$. Values below limit of quantification were set to zero (and can be used to identity non-detects).
	\item Other meta-data: meta-data has been standardised.
	\item Temporal resolution: The temporal resolution of the database is 1 day. Date below this resolution has been aggregated by maximum.
	\item Validity Checks: Simple rules for validity checks have been implemented (e.g. no negative concentrations).
\end{enumerate}

@@

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width = 0.8\textwidth]{pmix}
	\caption{Distribution of the number of quantified compounds in the samples.}
	\label{fig:pmix}
\end{figure}
